\documentclass[]{Resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Pratik}{Pathak}{ \urlstyle{same}\href{http://pratikpathak.me}{pratikpathak.me }| \href{https://www.linkedin.com/in/pathakpratik/}{linkedin.com/in/pathakpratik/}\\
\href{mailto:me@pratikpathak.com}{me@pratikpathak.com} | +919769151021
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{St. John College of \\
Engineer \& Management}
\descript{BE in Computer Science}
\location{July 2022 | Mumbai, IN}
\location{ Cum. GPA: 8.91 / 10.0}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/zpratikpathak}{zpratikpathak} \\
LinkedIn://  \href{https://www.linkedin.com/in/pathakpratik/}{in/pathakpratik/} \\
Website://  \href{https://pratikpathak.com/}{pratikpathak.com}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
\location{Versed:}
Python \textbullet{} Shell/Bash \textbullet{} Java \textbullet{} Javascript \\ 
\location{Comfortable:}
CSS \textbullet{} HTML \textbullet{} Linux \\
\subsection{Frameworks/Tools}
React \textbullet{}Azure \textbullet{} Docker \textbullet{} Nodejs \\
\textbullet{}Kubernetes \textbullet{} Git \textbullet{} Ansible \textbullet{}  MySQL \textbullet{} MongoDB 
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CERTIFICATION}
% \subsection{Microsoft}
% make the certificate name bold

\location{Microsoft Certified:}
Azure Administrative associate\\
\location{Microsoft Certified:}
Azure Data Scientist Associate\\
\location{Microsoft Certified:}
Azure AI Engineer Associate\\
\location{Microsoft Certified Trainer}
\location{Oracle Certified:}
Oracle Cloud Architect\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
\textbf{2022:} 2nd prize in C Coding Competition\\
\textbf{2022:} Speaker/Organiser 2 Day Workshop on Serverless Computing\\
\textbf{2022:} Speaker/Organiser 2 Day Workshop on Serverless Computing\\
\textbf{2020:} Hosted Machine Learning Seminar at VCET\\
\textbf{2022:} Def Hack | Global 2.0 - Mentor\\
\textbf{2022:} Finalist in Innovate for Assam Hackathon\\
\textbf{2021:} 6th Rank in national level "Online Python Coding Challenge"\\
\textbf{2021:} 11th Rank in Reva Hack Hackathon\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{TATA CONSULTANCY SERVICES}
\descript{| Full Stack Developer \& Lead }
\location{Jul 2022 - Present | Bangalore, IN}
\vspace{\topsep}
\begin{tightemize}
\item Worked as \textbf{Lead Developer}, Tech Stack Used : Python, JS, Nodejs, CSS, HTML, Jquery, Highcharts, Spotfire.
\item Update/Modify/Add/Remove Feature based on Client requirements.
\item Interected with Client Directly and understand their requirements.
\item Collaborated with multiple team for particular feature development.
\end{tightemize}
\sectionsep

\runsubsection{CRMNEXT}
\descript{| Quality Analyst Engineer }
\location{Dec 2021 – Mar 2022 | Mumbai, IN}
\begin{tightemize}
\item Joined as Automation Tester. Tech Stack Used: Python, Selenium, JS, HTML
\item Developed scripts for automation testing and performed UAT/testing of application to satisfy user demands.
\end{tightemize}
\sectionsep

\runsubsection{Microsoft}
\descript{| Microsoft Certified Trainer }
\location{Aug 2020 – Present | IN}
\begin{tightemize}
\item Worked as Freelance Corporate Trainer and provided training on Azure Cloud, Azure Administrator, Azure Developer, etc.
\item Hosted/Organised many workshops/seminar for student at no charge.
\end{tightemize}
\sectionsep

\runsubsection{Microsoft}
\descript{| Microsoft Student Learn Ambassador}
\location{Dec 2019 – May 2022 | Mumbai | IN}
\begin{tightemize}
\item Organised Workshops and Seminars for Student under Microsoft Student Learn Ambassador. Communicated with many Industry Experts and Started public speaking and delivered many lectures in open source communities.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{PRIVATE ECOSYSTEM}
\location{}
\textbf{DeploymentServer:} Created personal deployment server on which we can deploy using multiple tech stack [pratikpathak.com:8090].\\
\textbf{CloudDrive:} Personal cloud storage with all the features inspired from GMeet \& GDrive[cloud.pratikpathak.com].\\
\textbf{Blog:} Self Hosted Personal Bloging Website [pratikpathak.com]\\
\textbf{Mail:} Mail Server with all email functionality [mail.pratikpathak.com].
\sectionsep

\runsubsection{FAKE NEWS DETECTION EXTENSION}
\location{}
Created a chrome extension which accepts news as an input and predict whether the given news is fake or not.
\sectionsep

\runsubsection{IMAGE ALTERATION DETECTOR}
\location{}
A software capable of evaluating whether the image being used has been tampered or not.
\sectionsep

\runsubsection{LOCAL CONNECT}
\location{}
A private Local chat web server accessible all the people who are connected to this network can access.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2019	     & 3\textsuperscript{rd}/400+   & Won Hackstomp National Hackathon\\
2020	     & 2\textsuperscript{nd}/120+   & Won 2nd in Debugging Competition\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
